---
title: "prob2"
author: "daisy_gui"
date: "2025-10-30"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

This is a dataset on airbnb in NYC. Only entire home/apt in Bronx which price is lower than $1000 is filtered. 

```{r}
data(nyc_airbnb)

airbnb_df = nyc_airbnb %>%
  filter(
    neighbourhood_group == "Bronx",
    room_type == "Entire home/apt", 
    price < 1000)
```

This code plots a scatter plot on review_score_location and number of views.The color represents the price. 

```{r}
plot_ly(
  airbnb_df, 
  x = ~number_of_reviews, y = ~review_scores_location, 
  type = "scatter", mode = "markers", color = ~price, alpha = 0.5
)
```

This boxplot below shows nuber of reviews of airbnb in different neighbourhoods in Bronx. 

```{r}
plot_ly(
  airbnb_df,
  y = ~number_of_reviews, 
  color = ~neighbourhood, type = "box"
  )
```

This barchart shows the review per month in different neibourhood in bronx of popular airbnbs which have more than 5 reviews per month. 

```{r}
pop_airbnb = filter(airbnb_df, reviews_per_month > 5)

plot_ly(
  pop_airbnb, 
  x = ~reviews_per_month, y = ~neighbourhood, 
  color = ~neighbourhood, type = "bar", 
  orientation = "h"
        )
```

